---
title: "Stick Figure Animation"
author: "Billy Lozowski"
date: "`r Sys.Date()`"
output: html_document
---

If this is the first time using it, install gganimate -  install.packages("gganimate")

```{r Setup, include=FALSE}
# Load the required packages from the library
library(readr)
library(tidyverse)
library(gganimate)
# library(plotly) # this will be used when creating a 3D figure
```

# Load the time series and the existing event data (if already calculated)

```{r Load Data}
file_path <- file.choose() # choose the file
df <- read.delim(file_path, header = TRUE, skip = 8, check.names = FALSE) # read in the table and remove the first 8 rows
file_name <- tools::file_path_sans_ext(basename(file_path)) # extract he file name

df$Time <- df$`Sample #` * 0.01 # create a time column dependent on sampling freq.
df <- df %>%
  select(-83)
df <- df %>%
  select(Time, everything()) %>% # reorganise so time is the first column
  select(-33:-44, -57:-59) # remove ASIS and PSIS columns

file_path <- file.choose() # choose the .csv file with the event data in it
df_events <- read.csv(file_path)

```

## If time series data has not been event marked, and indices have not been calculated, remove "eval=FALSE" and run this code chunk.

```{r Event Mark & Trim, eval=FALSE}
# FFC
FFC_index <- which(df$`Event - FFC` > 20)[1] # adjust threshold as necessary

# BFC1 - ankle acceleration in the Y (vertical)
# BFC2 - ankle velocity in the X (anteroposterior)

subset_data_BFC2 <- df[1:FFC_index, ] # Subset the data frame from the start to FFC_index

# Find the index of the maximum value in "Event - BFC2" within the subsetted data
BFC2_index <- which.max(ifelse(is.na(subset_data_BFC2$`Event - BFC2`), -Inf, subset_data_BFC2$`Event - BFC2`))
# Subset the data frame from the maximum BFC_1 index to the end (may be better to FFC_index)
subset_data_BFC1 <- df[(BFC2_index + 1):nrow(df), ]
# Find the first occurrence where BFC1 goes from negative to positive
BFC1_index <- which.max(diff(sign(subset_data_BFC1$`Event - BFC1`) > 0))
# Calculate the overall index in the original data frame
BFC_index <- BFC2_index + BFC1_index

# MAW
MAW_index <- which.min(df$`Event - MAW` == min(df$`Event - MAW`, na.rm = TRUE))[1]

# BR
BR_index <- which.max(df$`Event - BR`)[1]

# EFT
# Check if ball release has occurred
if (!is.na(BR_index) && BR_index < nrow(df)) {
  # Subset the data from ball release to ball release +100
  subset_data <- df[(BR_index + 10):(BR_index + 50), ]

  # Find the index of the row where FT is at its smallest in the subset
  EFT_index <- which(subset_data$`Event - EFT` == min(subset_data$`Event - EFT`, na.rm = TRUE))[1]
  
}

EFT_index <- (BR_index + 10) + EFT_index # determine event index in full data frame

# trimmed data frame
df_final <- df[BFC_index:EFT_index, ]
```

## Alternatively, you have the option to hard-code event indices below.

```{r Manually input event indices if known already, eval=FALSE}
BFC_index <-
FFC_index <-
MAW_index <-
BR_index <-
EFT_index <-
```

# Trim the data from BFC -25 frames to EFT +25 frames

When the event indices are already known, extract them from the specified "Events" column in the loaded .csv file. Use BFC and EFT to determine the length of the trial, and add a buffer of 25 frames to the beginning and end of the data frame.

```{r extract event indices from .csv file "Event Data"}
BFC_index <- df_events[1,4] # row 1, column 4
FFC_index <- df_events[2,4] # row 2, column 4
MAW_index <- df_events[3,4] # row 3, column 4
BR_index <- df_events[4,4]  # row 4, column 4
EFT_index <- df_events[5,4] # row 5, column 4

df_trimmed <- df[(BFC_index-25):(EFT_index+25), ] # use this code if you want to trim the df with a buffer to the motion's duration. Adjust buffer (+- 25) as required. Save this as a new .csv
```

# Time normalise the trimmed trial data

Convert the trimmed data frame to 101 rows so that when plotting multiple throws together, they are all roughly the same length.

```{r Time-normalise trimmed data}
# Define the function for time normalising
time_normalise <- function(data) {
  # Get the number of rows in the original data
  n <- nrow(data)
  
  # Original time vector based on the number of rows
  original_time <- seq(0, n - 1)
  
  # Define the target time vector for 101 points
  target_time <- seq(0, n - 1, length.out = 101)  # 101 evenly spaced points
  
  # Initialize a data frame to store the interpolated data
  interpolated_data <- data.frame(matrix(nrow = 101, ncol = ncol(data)))
  colnames(interpolated_data) <- colnames(data)  # Keep original column names
  
  # Perform interpolation for each column of the data
  for (col in 1:ncol(data)) {
    current_col_data <- data[[col]]  # Access the column directly
    
    # Perform interpolation, ensuring we handle NAs if any exist
    interpolated_values <- approx(original_time, current_col_data, xout = target_time, na.rm = TRUE)$y
    
    # Fill the interpolated data
    interpolated_data[, col] <- interpolated_values
  }
  
  # Add the Duration column (0 to 100)
  interpolated_data <- cbind(interpolated_data, Duration = seq(0, 100, length.out = 101))
  
  return(interpolated_data)
}

# Perform time normalisation
df_final <- time_normalise(df_trimmed)


# Save plot_data as CSV to the specified folder and file name
write.csv(df_trimmed, file = paste0(file_name, ".csv"), row.names = FALSE)
```

# Generate animated figure

Now that the data has been event marked, trimmed, and time-normalised, we can plot each row and animate. We create an object that stores each row plot (i.e. joint centre position data at row 1:row101), then use "animate" from gganimate to stitch these together. Once rendered, this will display in the 'Viewer' panel. We can also save the gif (although, playback of this saved version is quite low-resolution. I'd recommend opening the .html version and saving each gif from the web).

```{r Animated Stick Figure - side, include=FALSE}
stick_side <- ggplot(df_final) +
  
  # left leg
  geom_segment(aes(x = L_toe_X, y = L_toe_Y, xend = L_ankle_X, yend = L_ankle_Y),   # foot
               linewidth = 1.5, colour = '#FF0000') + 
  geom_segment(aes(x = L_ankle_X, y = L_ankle_Y, xend = L_knee_X, yend = L_knee_Y), # shank  
               linewidth = 1.5, colour = '#FF0000') + 
  geom_segment(aes(x = L_knee_X, y = L_knee_Y, xend = L_hip_X, yend = L_hip_Y),     # thigh 
               linewidth = 1.5, colour = '#FF0000') + 
  
  # left arm
  geom_segment(aes(x = L_shoulder_X, y = L_shoulder_Y, xend = L_elbow_X, yend = L_elbow_Y), # upper
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_elbow_X, y = L_elbow_Y, xend = L_wrist_X, yend = L_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_wrist_X, y = L_wrist_Y, xend = L_finger_X, yend = L_finger_Y),     # hand
               linewidth = 1.5, colour = '#FF0000') +
  
  # pelvis
  geom_segment(aes(x = R_hip_X, y = R_hip_Y, xend = L_hip_X, yend = L_hip_Y), 
               linewidth = 1.5) +         
  
  # lumbar spine
  geom_segment(aes(x = L5S1_X, y = L5S1_Y, xend = L1_X, yend = L1_Y),
               linewidth = 1.5) + 
  
  # thorax
  geom_segment(aes(x = C7T1_X, y = C7T1_Y, xend = L_shoulder_X, yend = L_shoulder_Y), 
               linewidth = 1.5) +          
  geom_segment(aes(x = L1_X, y = L1_Y, xend = L_shoulder_X, yend = L_shoulder_Y),
               linewidth = 1.5) +              
  geom_segment(aes(x = L1_X, y = L1_Y, xend = C7T1_X, yend = C7T1_Y), 
               linewidth = 1.5) +                          
  geom_segment(aes(x = C7T1_X, y = C7T1_Y, xend = R_shoulder_X, yend = R_shoulder_Y), 
               linewidth = 1.5) +          
  geom_segment(aes(x = L1_X, y = L1_Y, xend = R_shoulder_X, yend = R_shoulder_Y), 
               linewidth = 1.5) + 
  
  # right leg
  geom_segment(aes(x = R_toe_X, y = R_toe_Y, xend = R_ankle_X, yend = R_ankle_Y),   # foot
               linewidth = 1.5, colour = '#0800FF') +     
  geom_segment(aes(x = R_ankle_X, y = R_ankle_Y, xend = R_knee_X, yend = R_knee_Y), # shank
               linewidth = 1.5, colour = '#0800FF') +   
  geom_segment(aes(x = R_knee_X, y = R_knee_Y, xend = R_hip_X, yend = R_hip_Y),     # thigh
               linewidth = 1.5, colour = '#0800FF') +       
 
  # right arm
  geom_segment(aes(x = R_shoulder_X, y = R_shoulder_Y, xend = R_elbow_X, yend = R_elbow_Y), # upper
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_elbow_X, y = R_elbow_Y, xend = R_wrist_X, yend = R_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_wrist_X, y = R_wrist_Y, xend = R_finger_X, yend = R_finger_Y),     # hand
               linewidth = 1.5, colour = '#0800FF') +
  
  # set theme
  theme_void() +
  labs(x = NULL,
       y = NULL) +
  coord_fixed(ratio = 1) + # set the x to y axis ratio as 1 (x = y)
  transition_time(`Sample #`)

  # render the stick figure animation 
  animate(stick_side, nframes = 100, fps = 30, renderer = gifski_renderer())
  
  # save the animation
# anim_save(paste0(file_name, " (side).gif"), stick_side)
```

```{r Animated Stick Figure - front, include=FALSE}
stick_front <- ggplot(df_final) +
  
  # left leg
  geom_segment(aes(x = L_toe_Z, y = L_toe_Y, xend = L_ankle_Z, yend = L_ankle_Y),   # foot
               linewidth = 1.5, colour = '#FF0000') +     
  geom_segment(aes(x = L_ankle_Z, y = L_ankle_Y, xend = L_knee_Z, yend = L_knee_Y), # shank
               linewidth = 1.5, colour = '#FF0000') +     
  geom_segment(aes(x = L_knee_Z, y = L_knee_Y, xend = L_hip_Z, yend = L_hip_Y),     # thigh 
               linewidth = 1.5, colour = '#FF0000') +       
  
  # left arm
  geom_segment(aes(x = L_shoulder_Z, y = L_shoulder_Y, xend = L_elbow_Z, yend = L_elbow_Y), # upper
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_elbow_Z, y = L_elbow_Y, xend = L_wrist_Z, yend = L_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_wrist_Z, y = L_wrist_Y, xend = L_finger_Z, yend = L_finger_Y),     # hand
               linewidth = 1.5, colour = '#FF0000') +
  
  # pelvis
  geom_segment(aes(x = R_hip_Z, y = R_hip_Y, xend = L_hip_Z, yend = L_hip_Y), 
               linewidth = 1.5) +
  
  # lumbar spine
  geom_segment(aes(x = L5S1_Z, y = L5S1_Y, xend = L1_Z, yend = L1_Y), 
               linewidth = 1.5) +
  
  # thorax
  geom_segment(aes(x = C7T1_Z, y = C7T1_Y, xend = L_shoulder_Z, yend = L_shoulder_Y), 
               linewidth = 1.5) +
  geom_segment(aes(x = L1_Z, y = L1_Y, xend = L_shoulder_Z, yend = L_shoulder_Y), 
               linewidth = 1.5) +
  geom_segment(aes(x = L1_Z, y = L1_Y, xend = C7T1_Z, yend = C7T1_Y), 
               linewidth = 1.5) +
  geom_segment(aes(x = C7T1_Z, y = C7T1_Y, xend = R_shoulder_Z, yend = R_shoulder_Y), 
               linewidth = 1.5) +
  geom_segment(aes(x = L1_Z, y = L1_Y, xend = R_shoulder_Z, yend = R_shoulder_Y), 
               linewidth = 1.5) +    
  
  # right leg
  geom_segment(aes(x = R_toe_Z, y = R_toe_Y, xend = R_ankle_Z, yend = R_ankle_Y),   # foot
               linewidth = 1.5, colour = '#0800FF') +     # right foot 
  geom_segment(aes(x = R_ankle_Z, y = R_ankle_Y, xend = R_knee_Z, yend = R_knee_Y), # shank
               linewidth = 1.5, colour = '#0800FF') +   
  geom_segment(aes(x = R_knee_Z, y = R_knee_Y, xend = R_hip_Z, yend = R_hip_Y),     # thigh
               linewidth = 1.5, colour = '#0800FF') +       
 
  # right arm
  geom_segment(aes(x = R_shoulder_Z, y = R_shoulder_Y, xend = R_elbow_Z, yend = R_elbow_Y), # upper
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_elbow_Z, y = R_elbow_Y, xend = R_wrist_Z, yend = R_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_wrist_Z, y = R_wrist_Y, xend = R_finger_Z, yend = R_finger_Y),     # hand
               linewidth = 1.5, colour = '#0800FF') +
  
  # set theme
  theme_void() +
  labs(x = NULL,
       y = NULL) +
  scale_x_reverse() +  # Flip the figure horizontally
  coord_fixed(ratio = 1) +
  transition_time(`Sample #`)

  # render the stick figure animation 
  animate(stick_front, nframes = 100, fps = 30, renderer = gifski_renderer())
  
  # save the animation
# anim_save(paste0(file_name, " (front).gif"), stick_front)
```  
  
```{r BFC, include=FALSE}
df_BFC <- df[BFC_index, ]

# side view
stick_BFC_side <- ggplot(df_BFC) +
  
  # left leg
  geom_segment(aes(x = L_toe_X, y = L_toe_Y, xend = L_ankle_X, yend = L_ankle_Y),   # foot
               linewidth = 1.5, colour = '#FF0000') + 
  geom_segment(aes(x = L_ankle_X, y = L_ankle_Y, xend = L_knee_X, yend = L_knee_Y), # shank  
               linewidth = 1.5, colour = '#FF0000') + 
  geom_segment(aes(x = L_knee_X, y = L_knee_Y, xend = L_hip_X, yend = L_hip_Y),     # thigh 
               linewidth = 1.5, colour = '#FF0000') + 
  
  # left arm
  geom_segment(aes(x = L_shoulder_X, y = L_shoulder_Y, xend = L_elbow_X, yend = L_elbow_Y), # upper
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_elbow_X, y = L_elbow_Y, xend = L_wrist_X, yend = L_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_wrist_X, y = L_wrist_Y, xend = L_finger_X, yend = L_finger_Y),     # hand
               linewidth = 1.5, colour = '#FF0000') +
  
  # pelvis
  geom_segment(aes(x = R_hip_X, y = R_hip_Y, xend = L_hip_X, yend = L_hip_Y), 
               linewidth = 1.5) + 
  
  # lumbar spine
  geom_segment(aes(x = L5S1_X, y = L5S1_Y, xend = L1_X, yend = L1_Y), 
               linewidth = 1.5) +
  
  # thorax
  geom_segment(aes(x = C7T1_X, y = C7T1_Y, xend = L_shoulder_X, yend = L_shoulder_Y), 
               linewidth = 1.5) +
  geom_segment(aes(x = L1_X, y = L1_Y, xend = L_shoulder_X, yend = L_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_X, y = L1_Y, xend = C7T1_X, yend = C7T1_Y), 
               linewidth = 1.5) +  
  geom_segment(aes(x = C7T1_X, y = C7T1_Y, xend = R_shoulder_X, yend = R_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_X, y = L1_Y, xend = R_shoulder_X, yend = R_shoulder_Y), 
               linewidth = 1.5) +    
  
  # right leg
  geom_segment(aes(x = R_toe_X, y = R_toe_Y, xend = R_ankle_X, yend = R_ankle_Y),   # foot
               linewidth = 1.5, colour = '#0800FF') +     
  geom_segment(aes(x = R_ankle_X, y = R_ankle_Y, xend = R_knee_X, yend = R_knee_Y), # shank
               linewidth = 1.5, colour = '#0800FF') +   
  geom_segment(aes(x = R_knee_X, y = R_knee_Y, xend = R_hip_X, yend = R_hip_Y),     # thigh
               linewidth = 1.5, colour = '#0800FF') +       
 
  # right arm
  geom_segment(aes(x = R_shoulder_X, y = R_shoulder_Y, xend = R_elbow_X, yend = R_elbow_Y), # upper
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_elbow_X, y = R_elbow_Y, xend = R_wrist_X, yend = R_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_wrist_X, y = R_wrist_Y, xend = R_finger_X, yend = R_finger_Y),     # hand
               linewidth = 1.5, colour = '#0800FF') +
  
  # set theme
  theme_void() +
  labs(x = NULL,
       y = NULL) +
  coord_fixed(ratio = 1)

ggsave(stick_BFC_side, filename = paste0(file_name, " - BFC (side).png"), dpi = 600)

# front view
stick_BFC_front <- ggplot(df_BFC) +
  
  # left leg
  geom_segment(aes(x = L_toe_Z, y = L_toe_Y, xend = L_ankle_Z, yend = L_ankle_Y),   # foot
               linewidth = 1.5, colour = '#FF0000') +  
  geom_segment(aes(x = L_ankle_Z, y = L_ankle_Y, xend = L_knee_Z, yend = L_knee_Y), # shank  
               linewidth = 1.5, colour = '#FF0000') +   
  geom_segment(aes(x = L_knee_Z, y = L_knee_Y, xend = L_hip_Z, yend = L_hip_Y),     # thigh 
               linewidth = 1.5, colour = '#FF0000') +      
  
  # left arm
  geom_segment(aes(x = L_shoulder_Z, y = L_shoulder_Y, xend = L_elbow_Z, yend = L_elbow_Y), # upper
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_elbow_Z, y = L_elbow_Y, xend = L_wrist_Z, yend = L_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_wrist_Z, y = L_wrist_Y, xend = L_finger_Z, yend = L_finger_Y),     # hand
               linewidth = 1.5, colour = '#FF0000') +
  
  # pelvis
  geom_segment(aes(x = R_hip_Z, y = R_hip_Y, xend = L_hip_Z, yend = L_hip_Y), 
               linewidth = 1.5) +
  
  # lumbar spine
  geom_segment(aes(x = L5S1_Z, y = L5S1_Y, xend = L1_Z, yend = L1_Y), 
               linewidth = 1.5) +
  
  # thorax
  geom_segment(aes(x = C7T1_Z, y = C7T1_Y, xend = L_shoulder_Z, yend = L_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_Z, y = L1_Y, xend = L_shoulder_Z, yend = L_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_Z, y = L1_Y, xend = C7T1_Z, yend = C7T1_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = C7T1_Z, y = C7T1_Y, xend = R_shoulder_Z, yend = R_shoulder_Y), 
               linewidth = 1.5) +
  geom_segment(aes(x = L1_Z, y = L1_Y, xend = R_shoulder_Z, yend = R_shoulder_Y), 
               linewidth = 1.5) +    
  
  # right leg
  geom_segment(aes(x = R_toe_Z, y = R_toe_Y, xend = R_ankle_Z, yend = R_ankle_Y),   # foot
               linewidth = 1.5, colour = '#0800FF') +     
  geom_segment(aes(x = R_ankle_Z, y = R_ankle_Y, xend = R_knee_Z, yend = R_knee_Y), # shank
               linewidth = 1.5, colour = '#0800FF') +   
  geom_segment(aes(x = R_knee_Z, y = R_knee_Y, xend = R_hip_Z, yend = R_hip_Y),     # thigh
               linewidth = 1.5, colour = '#0800FF') +       
 
  # right arm
  geom_segment(aes(x = R_shoulder_Z, y = R_shoulder_Y, xend = R_elbow_Z, yend = R_elbow_Y), # upper
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_elbow_Z, y = R_elbow_Y, xend = R_wrist_Z, yend = R_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_wrist_Z, y = R_wrist_Y, xend = R_finger_Z, yend = R_finger_Y),     # hand
               linewidth = 1.5, colour = '#0800FF') +
  
  # set theme
  theme_void() +
  labs(x = NULL,
       y = NULL) +
  scale_x_reverse() +  # Flip the figure horizontally
  coord_fixed(ratio = 1)

ggsave(stick_BFC_front, filename = paste0(file_name, " - BFC (front).png"), dpi = 600)
```

```{r FFC, include=FALSE}
df_FFC <- df[FFC_index, ]

# side view
stick_FFC_side <- ggplot(df_FFC) +
  
  # left leg
  geom_segment(aes(x = L_toe_X, y = L_toe_Y, xend = L_ankle_X, yend = L_ankle_Y),   # foot
               linewidth = 1.5, colour = '#FF0000') + 
  geom_segment(aes(x = L_ankle_X, y = L_ankle_Y, xend = L_knee_X, yend = L_knee_Y), # shank  
               linewidth = 1.5, colour = '#FF0000') + 
  geom_segment(aes(x = L_knee_X, y = L_knee_Y, xend = L_hip_X, yend = L_hip_Y),     # thigh 
               linewidth = 1.5, colour = '#FF0000') + 
  
  # left arm
  geom_segment(aes(x = L_shoulder_X, y = L_shoulder_Y, xend = L_elbow_X, yend = L_elbow_Y), # upper
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_elbow_X, y = L_elbow_Y, xend = L_wrist_X, yend = L_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_wrist_X, y = L_wrist_Y, xend = L_finger_X, yend = L_finger_Y),     # hand
               linewidth = 1.5, colour = '#FF0000') +
  
  # pelvis
  geom_segment(aes(x = R_hip_X, y = R_hip_Y, xend = L_hip_X, yend = L_hip_Y), 
               linewidth = 1.5) + 
  
  # lumbar spine
  geom_segment(aes(x = L5S1_X, y = L5S1_Y, xend = L1_X, yend = L1_Y), 
               linewidth = 1.5) +
  
  # thorax
  geom_segment(aes(x = C7T1_X, y = C7T1_Y, xend = L_shoulder_X, yend = L_shoulder_Y), 
               linewidth = 1.5) +
  geom_segment(aes(x = L1_X, y = L1_Y, xend = L_shoulder_X, yend = L_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_X, y = L1_Y, xend = C7T1_X, yend = C7T1_Y), 
               linewidth = 1.5) +  
  geom_segment(aes(x = C7T1_X, y = C7T1_Y, xend = R_shoulder_X, yend = R_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_X, y = L1_Y, xend = R_shoulder_X, yend = R_shoulder_Y), 
               linewidth = 1.5) +    
  
  # right leg
  geom_segment(aes(x = R_toe_X, y = R_toe_Y, xend = R_ankle_X, yend = R_ankle_Y),   # foot
               linewidth = 1.5, colour = '#0800FF') +     
  geom_segment(aes(x = R_ankle_X, y = R_ankle_Y, xend = R_knee_X, yend = R_knee_Y), # shank
               linewidth = 1.5, colour = '#0800FF') +   
  geom_segment(aes(x = R_knee_X, y = R_knee_Y, xend = R_hip_X, yend = R_hip_Y),     # thigh
               linewidth = 1.5, colour = '#0800FF') +       
 
  # right arm
  geom_segment(aes(x = R_shoulder_X, y = R_shoulder_Y, xend = R_elbow_X, yend = R_elbow_Y), # upper
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_elbow_X, y = R_elbow_Y, xend = R_wrist_X, yend = R_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_wrist_X, y = R_wrist_Y, xend = R_finger_X, yend = R_finger_Y),     # hand
               linewidth = 1.5, colour = '#0800FF') +
  
  # set theme
  theme_void() +
  labs(x = NULL,
       y = NULL) +
  coord_fixed(ratio = 1)

ggsave(stick_FFC_side, filename = paste0(file_name, " - FFC (side).png"), dpi = 600)

# front
stick_FFC_front <- ggplot(df_FFC) +
  
  # left leg
  geom_segment(aes(x = L_toe_Z, y = L_toe_Y, xend = L_ankle_Z, yend = L_ankle_Y),   # foot
               linewidth = 1.5, colour = '#FF0000') +  
  geom_segment(aes(x = L_ankle_Z, y = L_ankle_Y, xend = L_knee_Z, yend = L_knee_Y), # shank  
               linewidth = 1.5, colour = '#FF0000') +   
  geom_segment(aes(x = L_knee_Z, y = L_knee_Y, xend = L_hip_Z, yend = L_hip_Y),     # thigh 
               linewidth = 1.5, colour = '#FF0000') +      
  
  # left arm
  geom_segment(aes(x = L_shoulder_Z, y = L_shoulder_Y, xend = L_elbow_Z, yend = L_elbow_Y), # upper
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_elbow_Z, y = L_elbow_Y, xend = L_wrist_Z, yend = L_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_wrist_Z, y = L_wrist_Y, xend = L_finger_Z, yend = L_finger_Y),     # hand
               linewidth = 1.5, colour = '#FF0000') +
  
  # pelvis
  geom_segment(aes(x = R_hip_Z, y = R_hip_Y, xend = L_hip_Z, yend = L_hip_Y), 
               linewidth = 1.5) +
  
  # lumbar spine
  geom_segment(aes(x = L5S1_Z, y = L5S1_Y, xend = L1_Z, yend = L1_Y), 
               linewidth = 1.5) +
  
  # thorax
  geom_segment(aes(x = C7T1_Z, y = C7T1_Y, xend = L_shoulder_Z, yend = L_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_Z, y = L1_Y, xend = L_shoulder_Z, yend = L_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_Z, y = L1_Y, xend = C7T1_Z, yend = C7T1_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = C7T1_Z, y = C7T1_Y, xend = R_shoulder_Z, yend = R_shoulder_Y), 
               linewidth = 1.5) +
  geom_segment(aes(x = L1_Z, y = L1_Y, xend = R_shoulder_Z, yend = R_shoulder_Y), 
               linewidth = 1.5) +    
  
  # right leg
  geom_segment(aes(x = R_toe_Z, y = R_toe_Y, xend = R_ankle_Z, yend = R_ankle_Y),   # foot
               linewidth = 1.5, colour = '#0800FF') +     
  geom_segment(aes(x = R_ankle_Z, y = R_ankle_Y, xend = R_knee_Z, yend = R_knee_Y), # shank
               linewidth = 1.5, colour = '#0800FF') +   
  geom_segment(aes(x = R_knee_Z, y = R_knee_Y, xend = R_hip_Z, yend = R_hip_Y),     # thigh
               linewidth = 1.5, colour = '#0800FF') +       
 
  # right arm
  geom_segment(aes(x = R_shoulder_Z, y = R_shoulder_Y, xend = R_elbow_Z, yend = R_elbow_Y), # upper
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_elbow_Z, y = R_elbow_Y, xend = R_wrist_Z, yend = R_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_wrist_Z, y = R_wrist_Y, xend = R_finger_Z, yend = R_finger_Y),     # hand
               linewidth = 1.5, colour = '#0800FF') +
  
  # set theme
  theme_void() +
  labs(x = NULL,
       y = NULL) +
  scale_x_reverse() +  # Flip the figure horizontally
  coord_fixed(ratio = 1)

ggsave(stick_FFC_front, filename = paste0(file_name, " - FFC (front).png"), dpi = 600)

```

```{r MAW, include=FALSE}
df_MAW <- df[MAW_index, ]

# side view
stick_MAW_side <- ggplot(df_MAW) +
  
  # left leg
  geom_segment(aes(x = L_toe_X, y = L_toe_Y, xend = L_ankle_X, yend = L_ankle_Y),   # foot
               linewidth = 1.5, colour = '#FF0000') + 
  geom_segment(aes(x = L_ankle_X, y = L_ankle_Y, xend = L_knee_X, yend = L_knee_Y), # shank  
               linewidth = 1.5, colour = '#FF0000') + 
  geom_segment(aes(x = L_knee_X, y = L_knee_Y, xend = L_hip_X, yend = L_hip_Y),     # thigh 
               linewidth = 1.5, colour = '#FF0000') + 
  
  # left arm
  geom_segment(aes(x = L_shoulder_X, y = L_shoulder_Y, xend = L_elbow_X, yend = L_elbow_Y), # upper
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_elbow_X, y = L_elbow_Y, xend = L_wrist_X, yend = L_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_wrist_X, y = L_wrist_Y, xend = L_finger_X, yend = L_finger_Y),     # hand
               linewidth = 1.5, colour = '#FF0000') +
  
  # pelvis
  geom_segment(aes(x = R_hip_X, y = R_hip_Y, xend = L_hip_X, yend = L_hip_Y), 
               linewidth = 1.5) + 
  
  # lumbar spine
  geom_segment(aes(x = L5S1_X, y = L5S1_Y, xend = L1_X, yend = L1_Y), 
               linewidth = 1.5) +
  
  # thorax
  geom_segment(aes(x = C7T1_X, y = C7T1_Y, xend = L_shoulder_X, yend = L_shoulder_Y), 
               linewidth = 1.5) +
  geom_segment(aes(x = L1_X, y = L1_Y, xend = L_shoulder_X, yend = L_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_X, y = L1_Y, xend = C7T1_X, yend = C7T1_Y), 
               linewidth = 1.5) +  
  geom_segment(aes(x = C7T1_X, y = C7T1_Y, xend = R_shoulder_X, yend = R_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_X, y = L1_Y, xend = R_shoulder_X, yend = R_shoulder_Y), 
               linewidth = 1.5) +    
  
  # right leg
  geom_segment(aes(x = R_toe_X, y = R_toe_Y, xend = R_ankle_X, yend = R_ankle_Y),   # foot
               linewidth = 1.5, colour = '#0800FF') +     
  geom_segment(aes(x = R_ankle_X, y = R_ankle_Y, xend = R_knee_X, yend = R_knee_Y), # shank
               linewidth = 1.5, colour = '#0800FF') +   
  geom_segment(aes(x = R_knee_X, y = R_knee_Y, xend = R_hip_X, yend = R_hip_Y),     # thigh
               linewidth = 1.5, colour = '#0800FF') +       
 
  # right arm
  geom_segment(aes(x = R_shoulder_X, y = R_shoulder_Y, xend = R_elbow_X, yend = R_elbow_Y), # upper
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_elbow_X, y = R_elbow_Y, xend = R_wrist_X, yend = R_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_wrist_X, y = R_wrist_Y, xend = R_finger_X, yend = R_finger_Y),     # hand
               linewidth = 1.5, colour = '#0800FF') +
  
  # set theme
  theme_void() +
  labs(x = NULL,
       y = NULL) +
  coord_fixed(ratio = 1)

ggsave(stick_MAW_side, filename = paste0(file_name, " - MAW (side).png"), dpi = 600)

# front view
stick_MAW_front <- ggplot(df_MAW) +
  
  # left leg
  geom_segment(aes(x = L_toe_Z, y = L_toe_Y, xend = L_ankle_Z, yend = L_ankle_Y),   # foot
               linewidth = 1.5, colour = '#FF0000') +  
  geom_segment(aes(x = L_ankle_Z, y = L_ankle_Y, xend = L_knee_Z, yend = L_knee_Y), # shank  
               linewidth = 1.5, colour = '#FF0000') +   
  geom_segment(aes(x = L_knee_Z, y = L_knee_Y, xend = L_hip_Z, yend = L_hip_Y),     # thigh 
               linewidth = 1.5, colour = '#FF0000') +      
  
  # left arm
  geom_segment(aes(x = L_shoulder_Z, y = L_shoulder_Y, xend = L_elbow_Z, yend = L_elbow_Y), # upper
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_elbow_Z, y = L_elbow_Y, xend = L_wrist_Z, yend = L_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_wrist_Z, y = L_wrist_Y, xend = L_finger_Z, yend = L_finger_Y),     # hand
               linewidth = 1.5, colour = '#FF0000') +
  
  # pelvis
  geom_segment(aes(x = R_hip_Z, y = R_hip_Y, xend = L_hip_Z, yend = L_hip_Y), 
               linewidth = 1.5) +
  
  # lumbar spine
  geom_segment(aes(x = L5S1_Z, y = L5S1_Y, xend = L1_Z, yend = L1_Y), 
               linewidth = 1.5) +
  
  # thorax
  geom_segment(aes(x = C7T1_Z, y = C7T1_Y, xend = L_shoulder_Z, yend = L_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_Z, y = L1_Y, xend = L_shoulder_Z, yend = L_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_Z, y = L1_Y, xend = C7T1_Z, yend = C7T1_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = C7T1_Z, y = C7T1_Y, xend = R_shoulder_Z, yend = R_shoulder_Y), 
               linewidth = 1.5) +
  geom_segment(aes(x = L1_Z, y = L1_Y, xend = R_shoulder_Z, yend = R_shoulder_Y), 
               linewidth = 1.5) +    
  
  # right leg
  geom_segment(aes(x = R_toe_Z, y = R_toe_Y, xend = R_ankle_Z, yend = R_ankle_Y),   # foot
               linewidth = 1.5, colour = '#0800FF') +     
  geom_segment(aes(x = R_ankle_Z, y = R_ankle_Y, xend = R_knee_Z, yend = R_knee_Y), # shank
               linewidth = 1.5, colour = '#0800FF') +   
  geom_segment(aes(x = R_knee_Z, y = R_knee_Y, xend = R_hip_Z, yend = R_hip_Y),     # thigh
               linewidth = 1.5, colour = '#0800FF') +       
 
  # right arm
  geom_segment(aes(x = R_shoulder_Z, y = R_shoulder_Y, xend = R_elbow_Z, yend = R_elbow_Y), # upper
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_elbow_Z, y = R_elbow_Y, xend = R_wrist_Z, yend = R_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_wrist_Z, y = R_wrist_Y, xend = R_finger_Z, yend = R_finger_Y),     # hand
               linewidth = 1.5, colour = '#0800FF') +
  
  # set theme
  theme_void() +
  labs(x = NULL,
       y = NULL) +
  scale_x_reverse() +  # Flip the figure horizontally
  coord_fixed(ratio = 1)

ggsave(stick_MAW_front, filename = paste0(file_name, " - MAW (front).png"), dpi = 600)
```

```{r BR, include=FALSE}
df_BR <- df[BR_index, ]

# side view
stick_BR_side <- ggplot(df_BR) +
  
  # left leg
  geom_segment(aes(x = L_toe_X, y = L_toe_Y, xend = L_ankle_X, yend = L_ankle_Y),   # foot
               linewidth = 1.5, colour = '#FF0000') + 
  geom_segment(aes(x = L_ankle_X, y = L_ankle_Y, xend = L_knee_X, yend = L_knee_Y), # shank  
               linewidth = 1.5, colour = '#FF0000') + 
  geom_segment(aes(x = L_knee_X, y = L_knee_Y, xend = L_hip_X, yend = L_hip_Y),     # thigh 
               linewidth = 1.5, colour = '#FF0000') + 
  
  # left arm
  geom_segment(aes(x = L_shoulder_X, y = L_shoulder_Y, xend = L_elbow_X, yend = L_elbow_Y), # upper
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_elbow_X, y = L_elbow_Y, xend = L_wrist_X, yend = L_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_wrist_X, y = L_wrist_Y, xend = L_finger_X, yend = L_finger_Y),     # hand
               linewidth = 1.5, colour = '#FF0000') +
  
  # pelvis
  geom_segment(aes(x = R_hip_X, y = R_hip_Y, xend = L_hip_X, yend = L_hip_Y), 
               linewidth = 1.5) + 
  
  # lumbar spine
  geom_segment(aes(x = L5S1_X, y = L5S1_Y, xend = L1_X, yend = L1_Y), 
               linewidth = 1.5) +
  
  # thorax
  geom_segment(aes(x = C7T1_X, y = C7T1_Y, xend = L_shoulder_X, yend = L_shoulder_Y), 
               linewidth = 1.5) +
  geom_segment(aes(x = L1_X, y = L1_Y, xend = L_shoulder_X, yend = L_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_X, y = L1_Y, xend = C7T1_X, yend = C7T1_Y), 
               linewidth = 1.5) +  
  geom_segment(aes(x = C7T1_X, y = C7T1_Y, xend = R_shoulder_X, yend = R_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_X, y = L1_Y, xend = R_shoulder_X, yend = R_shoulder_Y), 
               linewidth = 1.5) +    
  
  # right leg
  geom_segment(aes(x = R_toe_X, y = R_toe_Y, xend = R_ankle_X, yend = R_ankle_Y),   # foot
               linewidth = 1.5, colour = '#0800FF') +     
  geom_segment(aes(x = R_ankle_X, y = R_ankle_Y, xend = R_knee_X, yend = R_knee_Y), # shank
               linewidth = 1.5, colour = '#0800FF') +   
  geom_segment(aes(x = R_knee_X, y = R_knee_Y, xend = R_hip_X, yend = R_hip_Y),     # thigh
               linewidth = 1.5, colour = '#0800FF') +       
 
  # right arm
  geom_segment(aes(x = R_shoulder_X, y = R_shoulder_Y, xend = R_elbow_X, yend = R_elbow_Y), # upper
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_elbow_X, y = R_elbow_Y, xend = R_wrist_X, yend = R_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_wrist_X, y = R_wrist_Y, xend = R_finger_X, yend = R_finger_Y),     # hand
               linewidth = 1.5, colour = '#0800FF') +
  
  # set theme
  theme_void() +
  labs(x = NULL,
       y = NULL) +
  coord_fixed(ratio = 1)

ggsave(stick_BR_side, filename = paste0(file_name, " - BR (side).png"), dpi = 600)

# front view
stick_BR_front <- ggplot(df_BR) +
  
  # left leg
  geom_segment(aes(x = L_toe_Z, y = L_toe_Y, xend = L_ankle_Z, yend = L_ankle_Y),   # foot
               linewidth = 1.5, colour = '#FF0000') +  
  geom_segment(aes(x = L_ankle_Z, y = L_ankle_Y, xend = L_knee_Z, yend = L_knee_Y), # shank  
               linewidth = 1.5, colour = '#FF0000') +   
  geom_segment(aes(x = L_knee_Z, y = L_knee_Y, xend = L_hip_Z, yend = L_hip_Y),     # thigh 
               linewidth = 1.5, colour = '#FF0000') +      
  
  # left arm
  geom_segment(aes(x = L_shoulder_Z, y = L_shoulder_Y, xend = L_elbow_Z, yend = L_elbow_Y), # upper
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_elbow_Z, y = L_elbow_Y, xend = L_wrist_Z, yend = L_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_wrist_Z, y = L_wrist_Y, xend = L_finger_Z, yend = L_finger_Y),     # hand
               linewidth = 1.5, colour = '#FF0000') +
  
  # pelvis
  geom_segment(aes(x = R_hip_Z, y = R_hip_Y, xend = L_hip_Z, yend = L_hip_Y), 
               linewidth = 1.5) +
  
  # lumbar spine
  geom_segment(aes(x = L5S1_Z, y = L5S1_Y, xend = L1_Z, yend = L1_Y), 
               linewidth = 1.5) +
  
  # thorax
  geom_segment(aes(x = C7T1_Z, y = C7T1_Y, xend = L_shoulder_Z, yend = L_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_Z, y = L1_Y, xend = L_shoulder_Z, yend = L_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_Z, y = L1_Y, xend = C7T1_Z, yend = C7T1_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = C7T1_Z, y = C7T1_Y, xend = R_shoulder_Z, yend = R_shoulder_Y), 
               linewidth = 1.5) +
  geom_segment(aes(x = L1_Z, y = L1_Y, xend = R_shoulder_Z, yend = R_shoulder_Y), 
               linewidth = 1.5) +    
  
  # right leg
  geom_segment(aes(x = R_toe_Z, y = R_toe_Y, xend = R_ankle_Z, yend = R_ankle_Y),   # foot
               linewidth = 1.5, colour = '#0800FF') +     
  geom_segment(aes(x = R_ankle_Z, y = R_ankle_Y, xend = R_knee_Z, yend = R_knee_Y), # shank
               linewidth = 1.5, colour = '#0800FF') +   
  geom_segment(aes(x = R_knee_Z, y = R_knee_Y, xend = R_hip_Z, yend = R_hip_Y),     # thigh
               linewidth = 1.5, colour = '#0800FF') +       
 
  # right arm
  geom_segment(aes(x = R_shoulder_Z, y = R_shoulder_Y, xend = R_elbow_Z, yend = R_elbow_Y), # upper
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_elbow_Z, y = R_elbow_Y, xend = R_wrist_Z, yend = R_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_wrist_Z, y = R_wrist_Y, xend = R_finger_Z, yend = R_finger_Y),     # hand
               linewidth = 1.5, colour = '#0800FF') +
  
  # set theme
  theme_void() +
  labs(x = NULL,
       y = NULL) +
  scale_x_reverse() +  # Flip the figure horizontally
  coord_fixed(ratio = 1)

ggsave(stick_BR_front, filename = paste0(file_name, " - BR (front).png"), dpi = 600)
```

```{r EFT, include=FALSE}
df_EFT <- df[EFT_index, ]

# side view
stick_EFT_side <- ggplot(df_EFT) +
  
  # left leg
  geom_segment(aes(x = L_toe_X, y = L_toe_Y, xend = L_ankle_X, yend = L_ankle_Y),   # foot
               linewidth = 1.5, colour = '#FF0000') + 
  geom_segment(aes(x = L_ankle_X, y = L_ankle_Y, xend = L_knee_X, yend = L_knee_Y), # shank  
               linewidth = 1.5, colour = '#FF0000') + 
  geom_segment(aes(x = L_knee_X, y = L_knee_Y, xend = L_hip_X, yend = L_hip_Y),     # thigh 
               linewidth = 1.5, colour = '#FF0000') + 
  
  # left arm
  geom_segment(aes(x = L_shoulder_X, y = L_shoulder_Y, xend = L_elbow_X, yend = L_elbow_Y), # upper
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_elbow_X, y = L_elbow_Y, xend = L_wrist_X, yend = L_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_wrist_X, y = L_wrist_Y, xend = L_finger_X, yend = L_finger_Y),     # hand
               linewidth = 1.5, colour = '#FF0000') +
  
  # pelvis
  geom_segment(aes(x = R_hip_X, y = R_hip_Y, xend = L_hip_X, yend = L_hip_Y), 
               linewidth = 1.5) + 
  
  # lumbar spine
  geom_segment(aes(x = L5S1_X, y = L5S1_Y, xend = L1_X, yend = L1_Y), 
               linewidth = 1.5) +
  
  # thorax
  geom_segment(aes(x = C7T1_X, y = C7T1_Y, xend = L_shoulder_X, yend = L_shoulder_Y), 
               linewidth = 1.5) +
  geom_segment(aes(x = L1_X, y = L1_Y, xend = L_shoulder_X, yend = L_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_X, y = L1_Y, xend = C7T1_X, yend = C7T1_Y), 
               linewidth = 1.5) +  
  geom_segment(aes(x = C7T1_X, y = C7T1_Y, xend = R_shoulder_X, yend = R_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_X, y = L1_Y, xend = R_shoulder_X, yend = R_shoulder_Y), 
               linewidth = 1.5) +    
  
  # right leg
  geom_segment(aes(x = R_toe_X, y = R_toe_Y, xend = R_ankle_X, yend = R_ankle_Y),   # foot
               linewidth = 1.5, colour = '#0800FF') +     
  geom_segment(aes(x = R_ankle_X, y = R_ankle_Y, xend = R_knee_X, yend = R_knee_Y), # shank
               linewidth = 1.5, colour = '#0800FF') +   
  geom_segment(aes(x = R_knee_X, y = R_knee_Y, xend = R_hip_X, yend = R_hip_Y),     # thigh
               linewidth = 1.5, colour = '#0800FF') +       
 
  # right arm
  geom_segment(aes(x = R_shoulder_X, y = R_shoulder_Y, xend = R_elbow_X, yend = R_elbow_Y), # upper
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_elbow_X, y = R_elbow_Y, xend = R_wrist_X, yend = R_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_wrist_X, y = R_wrist_Y, xend = R_finger_X, yend = R_finger_Y),     # hand
               linewidth = 1.5, colour = '#0800FF') +
  
  # set theme
  theme_void() +
  labs(x = NULL,
       y = NULL) +
  coord_fixed(ratio = 1)

ggsave(stick_EFT_side, filename = paste0(file_name, " - EFT (side).png"), dpi = 600)

# front view
stick_EFT_front <- ggplot(df_EFT) +
  
  # left leg
  geom_segment(aes(x = L_toe_Z, y = L_toe_Y, xend = L_ankle_Z, yend = L_ankle_Y),   # foot
               linewidth = 1.5, colour = '#FF0000') +  
  geom_segment(aes(x = L_ankle_Z, y = L_ankle_Y, xend = L_knee_Z, yend = L_knee_Y), # shank  
               linewidth = 1.5, colour = '#FF0000') +   
  geom_segment(aes(x = L_knee_Z, y = L_knee_Y, xend = L_hip_Z, yend = L_hip_Y),     # thigh 
               linewidth = 1.5, colour = '#FF0000') +      
  
  # left arm
  geom_segment(aes(x = L_shoulder_Z, y = L_shoulder_Y, xend = L_elbow_Z, yend = L_elbow_Y), # upper
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_elbow_Z, y = L_elbow_Y, xend = L_wrist_Z, yend = L_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#FF0000') +
  geom_segment(aes(x = L_wrist_Z, y = L_wrist_Y, xend = L_finger_Z, yend = L_finger_Y),     # hand
               linewidth = 1.5, colour = '#FF0000') +
  
  # pelvis
  geom_segment(aes(x = R_hip_Z, y = R_hip_Y, xend = L_hip_Z, yend = L_hip_Y), 
               linewidth = 1.5) +
  
  # lumbar spine
  geom_segment(aes(x = L5S1_Z, y = L5S1_Y, xend = L1_Z, yend = L1_Y), 
               linewidth = 1.5) +
  
  # thorax
  geom_segment(aes(x = C7T1_Z, y = C7T1_Y, xend = L_shoulder_Z, yend = L_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_Z, y = L1_Y, xend = L_shoulder_Z, yend = L_shoulder_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = L1_Z, y = L1_Y, xend = C7T1_Z, yend = C7T1_Y), 
               linewidth = 1.5) + 
  geom_segment(aes(x = C7T1_Z, y = C7T1_Y, xend = R_shoulder_Z, yend = R_shoulder_Y), 
               linewidth = 1.5) +
  geom_segment(aes(x = L1_Z, y = L1_Y, xend = R_shoulder_Z, yend = R_shoulder_Y), 
               linewidth = 1.5) +    
  
  # right leg
  geom_segment(aes(x = R_toe_Z, y = R_toe_Y, xend = R_ankle_Z, yend = R_ankle_Y),   # foot
               linewidth = 1.5, colour = '#0800FF') +     
  geom_segment(aes(x = R_ankle_Z, y = R_ankle_Y, xend = R_knee_Z, yend = R_knee_Y), # shank
               linewidth = 1.5, colour = '#0800FF') +   
  geom_segment(aes(x = R_knee_Z, y = R_knee_Y, xend = R_hip_Z, yend = R_hip_Y),     # thigh
               linewidth = 1.5, colour = '#0800FF') +       
 
  # right arm
  geom_segment(aes(x = R_shoulder_Z, y = R_shoulder_Y, xend = R_elbow_Z, yend = R_elbow_Y), # upper
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_elbow_Z, y = R_elbow_Y, xend = R_wrist_Z, yend = R_wrist_Y),       # forearm
               linewidth = 1.5, colour = '#0800FF') +
  geom_segment(aes(x = R_wrist_Z, y = R_wrist_Y, xend = R_finger_Z, yend = R_finger_Y),     # hand
               linewidth = 1.5, colour = '#0800FF') +
  
  # set theme
  theme_void() +
  labs(x = NULL,
       y = NULL) +
  scale_x_reverse() +  # Flip the figure horizontally
  coord_fixed(ratio = 1)

ggsave(stick_EFT_front, filename = paste0(file_name, " - EFT (front).png"), dpi = 600)
```